Cap-and-trade in Energy Capacity Investment when the planner is inattentive

### 2022-07-15 docs/Presentations/UVigo/home.Rmd
outline update

.pull-left[
- [Motivation](#motivation)
- [Why revisiting](#why)
- [Literature Review](#litrev)
- [Motivating example](#example)
- [Model](#model)
  - [Equilibrium](#equilibrium)
  <!-- - [Assumptions](#assumptions) -->
  - [Results](#results)
- [Discussion](#discussion)
]

.pull-right[
Extra
  - [Log case](#logcase)
  - [Beliefs](#resultsBeliefs)
]

>>>>

.pull-left[
- [Motivation](#motivation)
- [Model](#model)
- [Results](#results)
]
